---
title: "p8105_HW1"
author: "John Yang"
date: "2024-09-21"
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

```{r}
data("penguins", package = "palmerpenguins")
```

## Problem 1
### Description of Dataset
The dataset "penguins" consists of measurements and descriptions for three species of penguins. The following are the key variables:

  * `species` is a categorical variable describing the species of the penguin, which includes Adelie, Gentoo, and Chinstrap.
  * `island`is a categorical variable describing the island the penguin was identified on, which includes Torgersen, Biscoe, and Dream.
  * `bill_length_mm` is a continuous variable describing the length of the bill of penguin in millimeters.
  * `bill_depth_mm` is a continuous variable describing the depth of the bill of penguin in millimeters.
  * `flipper_length_mm` is an integer describing the length of the flipper of penguin in millimeters.
  * `body_mass_g`is an integer describing the mass of penguin in grams 
  * `sex` is a categorical variable describing the sex of the penguin, including male and female.
  * `year`is an integer describing the year of data recording.

This dataset contains **`r nrow(penguins)`** rows and **`r ncol(penguins)`** columns.

The mean flipper length is **`r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`** mm.

### Scatterplot of `flipper_length_mm` (y) vs `bill_length_mm` (x)
```{r yx_scatter, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)
```


## Problem 2
### Create a dataframe
```{r}
## set seed to ensure reproducibility
set.seed(12)

##define dataframe
hw1_df = tibble(
  norm_samp = rnorm(10), 
  logical_vec = norm_samp > 0,
  character_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(rep(c("lev1", "lev2", "lev3"), length.out = 10))
)
```

### Take the mean of each variable
```{r}
mean(pull(hw1_df, norm_samp))
mean(pull(hw1_df, logical_vec))
mean(pull(hw1_df, character_vec))
mean(pull(hw1_df, factor_vec))
```

Mean can be taken for numerical or logical vectors, such as norm_sample and logical_vec, but not for the character and factor vectors. 

### Explicitly converting variable from one type to another
```{r, message = FALSE, eval = FALSE}
as.numeric(pull(hw1_df, logical_vec))
as.numeric(pull(hw1_df, character_vec))
as.numeric(pull(hw1_df, factor_vec))
```

`as.numeric` function converted logical and factor vectors to numerical values. 
    Logical vectors became 0 and 1, where 1 represents true and 0 represents false.  
    Factor vectors became 1, 2, or 3 representing different levels.

`as.numeric` function did not work for the character vector. When the code was run, the warning message "NAs introduced by coercion" was given because R can not convert non-numeric strings to numbers. 

This explains the result of taking the mean with different variable types