---
title: "p8105_HW1"
author: "John Yang"
date: "2024-09-21"
output: github_document
---

```{r, echo = TRUE, message = FALSE}
library(tidyverse)
```

```{r}
data("penguins", package = "palmerpenguins")
```

## Problem 1
The dataset "penguins" consists of measurements and descriptions for three species of penguins. The following are the key variables:

  * `species` is a categorical variable describing the species of the penguin, which includes Adelie, Gentoo, and Chinstrap.
  * `island`is a categorical variable describing the island the penguin was identified on, which includes Torgersen, Biscoe, and Dream.
  * `bill_length_mm` is a continuous variable describing the length of the bill of penguin in millimeters.
  * `bill_depth_mm` is a continuous variable describing the depth of the bill of penguin in millimeters.
  * `flipper_length_mm` is an integer describing the length of the flipper of penguin in millimeters.
  * `body_mass_g`is an integer describing the mass of penguin in grams 
  * `sex` is a categorical variable describing the sex of the penguin, including male and female.
  * `year`is an integer describing the year of data recording.

This dataset contains `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm.


